How demand pattern identification and multicriteria ABC classification can guide management decisions

### 2024-01-17 manuscript/FCPCOM/manuscript.tex
updating introduction

Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}. Apresentar desvantagens e vantagens (citar livro produção enxuta). Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount \citep{Nirmala2022}.

Apresentar definição de contole de estoque.

As stated by \citep{Nirmala2022}, inventory control means well-organized management of raw materials and supplies, semi-finished goods and finished goods.

@@

>>>>

Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}. On the one hand the stock of raw materil, and finished and semi-finished goods serves to reduce the delivery time for the customer and ensure that possible failures in the process do not generate greater influence on production efficiency as well as delays in deliveries, on the other hand the stock usually represents a high cost, allocation of spaces that could be used for other purposes, possibilities of loss and depreciation, in addition to hiding process failures \citep{Shingo1996}. Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount, and the well-organized management of raw materials and supplies, semi-finished goods and finished goods is nominated Inventory Control \citep{Nirmala2022}.

@@

\bibitem[\protect\citeauthoryear{Shingo}{1996}]{Shingo1996}
Shingo, S. (1996). {\it O Sistema Toyota de Produção do ponto de vista da Engenharia de Produção}, tradução Eduardo Schaan, Ed. 2, Porto Alegre: Bookman.
